---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  error = TRUE
)

rlang::local_options(width = 80)
```

# *arg*: Clean and Simple Argument Checking
<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/arg)](https://CRAN.R-project.org/package=arg)
<!-- badges: end -->

*arg* produces nice, clean error messages for checking function arguments in R packages. I developed *arg* because I often found myself writing the same error messages in my packages, and I wasn't satisfied with the other similar R packages available. *arg* uses [*cli*](https://cli.r-lib.org/) to produce clean and clear errors without requiring much programming from the developer. These messages are designed to be clear to the user, not using complicated language. Many messages adapt to the type of (incorrect) input received.

*arg* contains function for common arguments checks, such as checking that an argument is a single number (`arg_number()`), a string (`arg_string()`), a single `TRUE`/`FALSE` value (`arg_flag()`), or a data frame or matrix (`arg_data()`). In addition, it is possible to build more complex argument checks using `arg_and()` and `arg_or()`, which require that all or at least one check is passed, and `when_not_null()` and `when_supplied()`, which allow for `NULL` or omitted arguments.

```{r}
library(arg)

z <- "a string"

# Check that `z` is a string
arg_string(z)

# Check that `z` is a number
arg_number(z)

# Check that `z` is a string of length 2
arg_and(z,
        arg_string,
        arg_length(2L))

# Check that `z` is NA, a flag, or a count
arg_or(z,
       arg_is_NA,
       arg_flag,
       arg_count)
```

*arg* is meant to be used inside other R packages. Its error-throwing function `err()` (a wrapper for `rlang::abort()`) automatically includes the relevant (user-facing) function in its error message.

The name "arg" is meant to be short for "argument", but also perhaps represents the sound you would make if you were to encounter an error when running some code. Hopefully *arg* reduces the number of times users say "arg!".

<!-- If you use any of my R packages, including [*MatchIt*], [*WeightIt*], [*cobalt*], [*optweight*], or [*adrftools*], you may already be using *arg*!
-->

## Installation

You can install the development version of *arg* from [GitHub](https://github.com/ngreifer/arg) with:

``` r
# install.packages("pak")
pak::pak("ngreifer/arg")
```

You can install the stable version on CRAN using

``` r
install.packages("arg")
```

## Related packages

*arg* serves a similar function to other existing packages. These packages may be better for your purposes, and *arg* is not meant to compete with them. 

* [*assertions*](https://selkamand.github.io/assertions/)
* [*checkmate*](https://mllg.github.io/checkmate/)
* [*checkarg*](https://cran.r-project.org/package=checkarg)
* [*chk*](https://poissonconsulting.github.io/chk/)
* [*dreamerr*](https://cran.r-project.org/package=dreamerr)
* [*erify*](https://flujoo.github.io/erify/)
* [*favr*](https://lj-jenkins.github.io/favr/)

